Scikit-learn: API design for machine learning

### 2013-06-19 paper.tex
rm Cython problems

Our implementation guidelines emphasize on writing efficient but readable code.
In particular, we focus on making the codebase easily maintainable and
understandable in order to favour external contributions. Whenever practicable,
algorithms implemented in \sklearn are thus directly written in pure Python. For
intensive numerical computations though, the library mostly relies on NumPy
vector operations, which allows for the code to remain concise, readable and
efficient. For all algorithms that cannot be easily and efficiently expressed as
NumPy operations, we rely on Cython \citep{behnel2011cython}  for writing the
critical parts and achieving decent performance and scalability. Cython is a
compiled programming language that extends Python with static typing. It
produces efficient C extension modules that are directly importable from the
Python run-time system. Examples of algorithms written in Cython include
stochastic gradient descent for linear models, some graph-based clustering
algorithms or decision trees.  A problem arising from the use of Cython,
however, is that passing pure Python functions as argument, while possible,
degrades performance significantly due to the run-time checks needed for each
function invocation. This is especially problematic for example for kernel
methods, which would benefit from accepting a kernel function as argument. A
potential solution to this problem would be for \sklearn to provide a Cython-level
API, thereby allowing the user to pass Cython-implemented kernel
functions.

>>>>

Our implementation guidelines emphasize on writing efficient but readable code.
In particular, we focus on making the codebase easily maintainable and
understandable in order to favour external contributions. Whenever practicable,
algorithms implemented in \sklearn are thus directly written in pure Python. For
intensive numerical computations though, the library mostly relies on NumPy
vector operations, which allows for the code to remain concise, readable and
efficient. For all algorithms that cannot be easily and efficiently expressed as
NumPy operations, we rely on Cython \citep{behnel2011cython}  for writing the
critical parts and achieving decent performance and scalability. Cython is a
compiled programming language that extends Python with static typing. It
produces efficient C extension modules that are directly importable from the
Python run-time system. Examples of algorithms written in Cython include
stochastic gradient descent for linear models, some graph-based clustering
algorithms and decision trees.
